Humanized Quadcopter Swarm System for IARC 2019

### 2019-06-01 IARC_Paper_2019/Paper.tex
I think done?

The eCalc online tool was used to validate our calculations, and as seen by the generated graph, there should be no issue reaching 8+ minute flight times at speeds below 15 [mph].

		\begin{figure}[!htbp]
			\begin{center}
				\includegraphics[width=0.6\textwidth]{powerGraph}
			\end{center}
		\end{figure}

@@

As for the 2000 [mAh] 3S battery, this battery powers our Pixhawk flight controller and our three Jetson TX2 compute units. This was done partly to dedicate the entirety of the main battery to propulsion to maximize flight time. The other reason is that the speed controllers we chose (T-Motor Air 40A) have no BEC, so a separate battery for the flight controller (and in turn the receiver) was the simplest solution. 2000 [mAh] was chosen because of the slim form factor we were able to find it in, and because it will provide more than adequate power while not adding any significant amount to the quad weight.

>>>>

The eCalc online tool was used to validate our calculations, and as seen by the graph on the following page, there should be no issue reaching flight times over 8 minutes at speeds below 15 [mph].

		\begin{figure}[!htbp]
			\begin{center}
				\includegraphics[width=\textwidth]{powerGraph}
			\end{center}
		\end{figure}

@@
